---
title: "Title of Project"
author: "Group # in Canvas; Student SIDs"
subtitle: "Project 2"
date: "University of Sydney | DATA1001 | September 2020"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary

<br>

# Full Report

## Initial Data Analysis (IDA)
Data cleaning was done in Excel. Unnecessary columns were removed and headings were replaced with simpler concise ones. The columns that were kept were: Score, Media Agencies, Check Frequency, Gender. Due to the need for a numerical analysis, more than 5 was considered as 5. Score formats were changed from e.g. "11 / 12" to "11". One entry had missing data and had to be removed.

```{r, warning=FALSE, message = FALSE}
# Read in your survey data
library(dplyr)
setwd("C:\\Users\\bigha\\OneDrive\\University Notes\\First Year SEM 2\\DATA1001\\Project 2\\")
survey = read.csv("COVID-19 Knowledge Survey - Copy.csv")
summary(survey)
```

<br>

## Research Questions 

<br>
Is there a linear correlation between the number of distinct media agencies an individual has gotten COVID-19 news from in the last month and the accuracy of their knowledge about COVID-19 facts.
```{r, message = FALSE}
library(ggplot2)
Score = survey$Score
Agencies = survey$Media.Agencies
Frequency = survey$Check.Frequency
Percentage = survey$Percentage
#Linear Model Plot
lmodel1 = lm(Percentage~Agencies)
summary(lmodel1)
ggplot(survey, aes(Media.Agencies, Percentage)) +
  geom_point() +
  geom_line(aes(y=predict(lmodel1))) +
  xlab("Number of unique Media Agencies individual acquired COVID-19 information from in past month") +
  ylab("Percentage Accuracy on COVID-19 Fact Test")
#Residuals Plot
ggplot(NULL, aes(survey$Media.Agencies, lmodel1$residuals)) +
  geom_point() +
  geom_hline(yintercept = 0) +
  labs(title = "Residuals Plot") +
  xlab("Number of unique Media Agencies individual acquired COVID-19 information from in past month") +
  ylab("Residuals") +
  geom_smooth()
#Correlation
cor(Agencies, Percentage)

```

If there a linear correlation between the frequency which an individual checks COVID-19 progression in the past month and the accuracy of their knowledge about COVID-19 facts.

```{r, message = FALSE}
#Linear Model Plot
lmodel2 = lm(Percentage~Frequency)
summary(lmodel1)
ggplot(survey, aes(Check.Frequency, Percentage)) +
  geom_point() +
  geom_line(aes(y=predict(lmodel2))) +
  xlab("Number of unique Media Agencies individual acquired COVID-19 information from in past month") +
  ylab("Percentage Accuracy on COVID-19 Fact Test")
#Residuals Plot
ggplot(NULL, aes(survey$Check.Frequency, lmodel1$residuals)) +
  geom_point() +
  geom_hline(yintercept = 0) +
  labs(title = "Residuals Plot") +
  xlab("Number of unique Media Agencies individual acquired COVID-19 information from in past month") +
  ylab("Residuals") +
  geom_smooth()
#Correlation
cor(Agencies, Percentage)
```

## Related Articles

<br>

## References
Use APA

<br>

## Acknowledgments
When did you team meet (date and time), and what did each team member contribute?








